Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-05-21 tse19/main.tex
quick pass on intro

\IEEEtitleabstractindextext{%
\begin{abstract}
Dealing with high testing costs remains an important problem in
Software Engineering.  Test suite parallelization is an important
approach to address this problem. \Mar{Sotero, vc. atualizou estas
  macros?}  Considering a set of \numSubjs{} Java projects we analyzed
from \github\, we found that \percentMedLongRunning{} of the them
contain long-running test suites, but parallelization features still
seem underutilized in practice~---~only \percentParallelUpdated{} of
projects with long-running test suites parallelize test
execution. According to a survey we conducted, the main reason for
adoption resistance was the concern to deal with concurrency issues
that could result in test flakiness.
%% This Results suggest that, on
%% average, developers prefer high predictability than high performance
%% in running tests.

@@

\IEEEPARstart{D}{ealing}
with high testing costs has been an important problem in
software engineering research and industrial practice.  Several
approaches have been proposed in the research literature to address
this problem, with the focus mainly on test suite minimization,
prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
In industry, the focus has been mainly on distributing the testing
workload.  Evidence of this are the Google TAP
system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
distributed infrastructures to efficiently build massive amounts of
code and run tests.  Building in-house server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the test suite of the Groupon PWA system, which powers
the \url{groupon.com} website, included over 19K tests.  To run all
those tests under 10m, Groupon used a cluster of 4 computers with 24
cores each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting cloud
services~\cite{cloud-services} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with modest
 or nonexistent budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware\Comment{ (\eg{}, existing workstations)} is an attractive
solution for running tests.  The proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable\Comment{ test execution} speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~inspired us to investigate 
test suite parallelization in practice.

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization to speed up testing in
open-source projects.  This is a relevant problem given the tremendous
popularity of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  Note that parallelization is
complementary to other approaches to mitigate testing costs such as
(safe) test
selection~\cite{Rothermel:1997:SER:248233.248262,gligoric-etal-issta2015}
and continuous integration~\cite{Saff:2003:RWD:951952.952340}.

The dimensions of analysis we considered in this study are (i)
feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects had short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practitioners to
the technology and to understand their reasons.  The dimension
\emph{speedup} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{tradeoffs} evaluates the relationship between speedups obtained
with parallelization and issues that arise 
when running tests in parallel, including test
flakiness~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  We briefly summarize our findings
in the following.

@@

% SECTION 2
\section{Parallel Execution of Test Suites}
Figure~\ref{fig:levels} illustrates different levels where
parallelism in test execution can be obtained.
The highest level indicates
parallelism obtained through different machines on the
network.  For instance, using virtual machines from a cloud service to
\begin{wrapfigure}{r}{0.13\textwidth}  
  \vspace{-2mm}
  \centering
  %  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}    
  \includegraphics[width=2cm]{figs/parallel-levels-short.pdf}  
  \caption{\label{fig:levels}Levels of parallelism.}
  \vspace{-2mm}
\end{wrapfigure}

>>>>

\IEEEtitleabstractindextext{%
\begin{abstract}
Dealing with high costs of testing remains an important problem in
Software Engineering.  Test suite parallelization is an important
approach to address this problem. \Mar{Sotero, vc. atualizou estas
  macros?}  Considering a set of \numSubjs{} Java projects we analyzed
from \github\, we found that \percentMedLongRunning{} of the them
contain long-running test suites, but parallelization features still
seem underutilized in practice~---~only \percentParallelUpdated{} of
projects with long-running test suites parallelize test
execution. According to a survey we conducted, the main reason for
adoption resistance was the concern to deal with concurrency issues
that could result in test flakiness.
%% This Results suggest that, on
%% average, developers prefer high predictability than high performance
%% in running tests.

@@

\IEEEPARstart{D}{ealing} with high testing costs has been an important
problem in software engineering research and industrial practice.
Several approaches have been proposed in the literature to address
this problem, with the focus mainly on test suite minimization,
prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
In industry, the focus has been mainly on distributing the testing
workload.  Evidence of this are the Google TAP
system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
distributed infrastructures to efficiently build massive amounts of
code and run tests.

%Distributing testing workloads in-house is also a
%viable solution at smaller-size organizations.

At large organizations, the alternative of renting cloud
services~\cite{cloud-services} or even building proprietary
infrastructures for building and running tests is a legitimate
approach to mitigate the regression testing problem.  For example, as
of August 2013, the test suite of the Groupon PWA system, which powers
the \url{groupon.com} website, included over 19K tests.  To run all
those tests under 10m, Groupon used a cluster of 4 computers with 24
cores each~\cite{kim-etal-fse2013}. However, for projects with modest
or nonexistent budgets and yet relatively heavy testing workloads,
this solution may not be economically viable.  For these cases, the
use of commodity hardware\Comment{ (\eg{}, existing workstations)} is
an attractive solution for running tests.  The proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable speedups through
increased CPU usage~(see Section~\ref{sec:background}).  These two
elements~---~demand for cost-effective test execution and supply of
relatively inexpensive testing infrastructures~---~inspired us to
investigate test suite parallelization in practice.

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization to speed up testing in
open-source projects.  This is a relevant problem given the tremendous
popularity of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  Note that parallelization is
complementary to other approaches to mitigate testing costs such as
(safe) test
selection~\cite{Rothermel:1997:SER:248233.248262,gligoric-etal-issta2015}
and continuous
integration~\cite{Saff:2003:RWD:951952.952340}.\Mar{revisit this later
  on...} In addition, we propose a solution to unleash the power of
test parallelization reducing (\Fix{eliminating?}) test flakiness due
to race conditions.

This study covers the following dimensions of interest
(i)~feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.
The dimension \emph{feasibility} measures the potential of
parallelization to reduce testing costs.  In the limit,
parallelization would be fruitless if all projects had short-running
test suites or if the execution cost was dominated by a single test
case in the suite.  The dimension \emph{adoption} evaluates how often
existing open-source projects use parallelization schemes and how
developers involved in costly projects---\ie{}, project not using test suite
parallelization---perceive this technology.  It is important to evaluate
resistance of practitioners to the technology and to understand their
reasons.  The \emph{speedup} dimension evaluates the observed impact
of parallelization in running times on projects that already use it.  Finally, the dimension
\emph{tradeoffs} evaluates the relationship between speedups obtained
with parallelization and issues that arise when running tests in
parallel, including test
flakiness~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  We briefly
summarize our findings in the following.

\Mar{We need to reorganize this a bit as to accomodate the new
  addition to the paper...}

@@

% SECTION 2
\section{\label{sec:background}Parallel Execution of Test Suites}
Figure~\ref{fig:levels} illustrates different levels where
parallelism in test execution can be obtained.
The highest level indicates
parallelism obtained through different machines on the
network.  For instance, using virtual machines from a cloud service to
\begin{wrapfigure}{r}{0.13\textwidth}  
  \vspace{-2mm}
  \centering
  %  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}    
  \includegraphics[width=2cm]{figs/parallel-levels-short.pdf}  
  \caption{\label{fig:levels}Levels of parallelism.}
  \vspace{-2mm}
\end{wrapfigure}
